### 2025-07-09 actuarial.qmd
20250702 - cross-validation
20250708 - track chunk execution times
20250709 - videos

@TPS2017 provides a video of sports pundits, Stephen A. Smith and Skip Bayless, making bold statements and incorrect predictions:

![Video of Sports Pundits, Stephen A. Smith and Skip Bayless, Making Bold Statements and Incorrect Predictions. From: <https://www.youtube.com/watch?v=lTjBuEPcLlc>.](images/sportsPundits.mp4){width=100%}\

@@

Cross-validation with large, representative samples can help evaluate the amount of shrinkage of estimates, particularly for more complex models such as [machine learning](#sec-machineLearning) models [@Ursenbach2019].
Ideally, cross-validation would be conducted with a separate sample (external cross-validation) to see the generalizability of estimates.
However, you can also do internal cross-validation.
For example, you can perform *k*-fold cross-validation, where you:

>>>>

::: {#fig-video-sports-pundits}

@TPS2017 provides a video of sports pundits, Stephen A. Smith and Skip Bayless, making bold statements and incorrect predictions, in @fig-video-sports-pundits:

{{< video images/sportsPundits.mp4 >}}

@@

Cross-validation with large, representative samples can help evaluate the amount of shrinkage of estimates, particularly for more complex models such as [machine learning](#sec-machineLearning) models [@Ursenbach2019].
Ideally, cross-validation would be conducted with a separate sample (external cross-validation) to see the generalizability of estimates.
However, you can also do internal cross-validation.
For example, you can perform [*k*-fold cross-validation](#sec-kFoldCrossValidation), where you:

### 2025-07-09 cognitive-bias.qmd
20250619 - calibration accuracy of projections
20250708 - track chunk execution times
20250709 - videos

Here is a video from @GetUpESPN2021 of Kyle Pitts drawing comparisons to the LeBron James of Tight Ends:

![Video of Kyle Pitts drawing comparisons to the LeBron James of Tight Ends. From: <https://x.com/GetUpESPN/status/1380165126108672001> (archived at <https://perma.cc/JW8E-KV2C>)](images/kylePitts.mp4){width=100%}\

@@

>>>>

::: {#fig-kyle-pitts}

A video from @GetUpESPN2021 (archived at <https://perma.cc/JW8E-KV2C>) of Kyle Pitts drawing comparisons to the LeBron James of Tight Ends is in @fig-kyle-pitts:

{{< video images/kylePitts.mp4 >}}

@@

With respect to fantasy football, projections of players' fantasy points tend to be overprecise, as described in @sec-accuracyProjections.
However, predictions about how well oneself will do in a fantasy football league may involve overestimation and overplacement.

### 2025-07-09 evaluating-prediction-accuracy.qmd
20250708 - videos and quotes
20250709 - videos

> "Nothing ruins fantasy more than reality." – [Renee Miller](https://www.youtube.com/watch?v=gmpLFWs5ae0&t=1430s) [@Yahoo2024]

>>>>

> "Nothing ruins fantasy more than reality." – [Renee Miller, Ph.D.](@fig-fantasy-vs-reality) [@Yahoo2024]

::: {.content-visible when-format="html:js"}

::: {#fig-fantasy-vs-reality}

{{< video https://www.youtube.com/watch?v=gmpLFWs5ae0 start="1430" >}}

### 2025-07-09 fantasy-football.qmd
20250708 - track chunk execution times
20250709 - videos

Here is a video that provides a brief introduction to American football [@Ly2015]:

![Video that Provides An Introduction to American Football. From: <https://www.youtube.com/watch?v=Ddwp1HyEFRE>.](images/football.mp4){width=100%}\

@@

Here is a video that provides a brief introduction to fantasy football [@NFLFantasy2020]:

![Video that Provides an Introduction to Fantasy Football. From: <https://www.youtube.com/watch?v=XhrBapdhLEc>.](images/fantasyFootball.mp4){width=100%}\

>>>>

::: {#fig-football-intro}

A video that provides a brief introduction to American football is in @fig-football-intro [@Ly2015]:

{{< video images/football.mp4 >}}

@@

::: {#fig-fantasy-football-intro}

A video that provides a brief introduction to fantasy football is in @fig-fantasy-football-intro [@NFLFantasy2020]:

{{< video images/fantasyFootball.mp4 >}}

### 2025-07-09 getting-started.qmd
20250709 - videos

::: {#nte-gettingStarted .callout-note title="If you are in Dr. Petersen's class"}
If you are in Dr. Petersen's class, also perform the following steps:

>>>>

::: {#nte-gettingStarted .callout-note title="If you are in Professor Petersen's class"}
If you are in Professor Petersen's class, also perform the following steps:

### 2025-07-09 intro.qmd
20250709 - videos

Here is a video of Professor Benjamin Motz that describes the value of teaching statistics through the lens of fantasy football [@NFL2014]:

![Video of Prof. Benjamin Motz Discussing Statistics and His Fantasy Football Course. From: <https://www.facebook.com/watch/?v=10155572257183615>.](images/motzVideo.mp4){width=100%}\

>>>>

A video of Professor Benjamin Motz that describes the value of teaching statistics through the lens of fantasy football is in @fig-video-motz [@NFL2014]:

{{< video images/motzVideo.mp4 >}}

### 2025-07-09 mixed-models.qmd
20250709 - videos

::: {#nte-bayesianMixedModelR2 .callout-note title="Bayesian mixed model R-sqaured"}
Note: the following code that estimates the $R^2$ for the Bayesian mixed model takes a while to run.
:::

>>>>

::: {#nte-bayesianMixedModelR2 .callout-note title="Bayesian mixed model R-squared"}
Note: the following code that estimates the $R^2$ for the Bayesian mixed model takes a while to run.
:::

### 2025-07-09 sports-cognitive-psychology.qmd
20250708 - track chunk execution times
20250709 - videos

For instance, here is a [2015 video clip](https://streamable.com/1hw8) of a football commentator, Mike Patrick, making fun of people who compile statistics for informing decision-making in football, calling the people who compile the numbers "guys who wear socks with flip-flops" [@ABC2015], suggesting that people who compile analytics to make recommendations in football are out of touch with the realities of football and do not have the same on-the-field understanding as the coaches and players.
The full game is [here](https://www.youtube.com/watch?v=1L9D2rp0mk8) [@ABC2015a].

![Football Commentator Making Fun of Analytics in Football. From: <https://streamable.com/1hw8> (2015).](images/commentatorOnAnalytics.mp4){width=100%}\

>>>>

::: {#fig-football-commentator}

For instance, there is a [2015 video clip](https://streamable.com/1hw8) of a football commentator, Mike Patrick, making fun of people who compile statistics for informing decision-making in football, calling the people who compile the numbers "guys who wear socks with flip-flops" in @fig-football-commentator [@ABC2015], suggesting that people who compile analytics to make recommendations in football are out of touch with the realities of football and do not have the same on-the-field understanding as the coaches and players.
The full game is [here](https://www.youtube.com/watch?v=1L9D2rp0mk8) [@ABC2015a].

{{< video images/commentatorOnAnalytics.mp4 >}}
